### 2025-07-21 decision-making.qmd
20250720 - fix

proportionZeroBracketingRate_seasonal <- seasonalIndividualSources %>% 
  filter(!is.na(bracketingRate)) %>% 
  mutate(isZeroBracketingRate = ifelse(bracketingRate == 0, 1, 0)) %>% 
  summarise(proportionZeroBracketingRate = sum(isZeroBracketingRate) / n())
```

@@

```{r}
weeklyIndividualSources %>% 
  filter(!is.na(bracketingRate)) %>% 
  mutate(isZeroBracketingRate = ifelse(bracketingRate == 0, 1, 0)) %>% 
  summarise(proportionZeroBracketingRate = sum(isZeroBracketingRate) / n())
```

@@

A key goal is to identify decisions that provide a net advantage in expected value.
Although there is considerable variability and the outcome is not guaranteed, small advantages can yield considerable gains in the long run @Tanney2021; however, one must be able to survive the costs of losses to obtain enough long-term trials.
So, do not bet more than you are willing to lose.

>>>>

proportionZeroBracketingRate_seasonal <- seasonalIndividualSources %>% 
  filter(!is.na(bracketingRate)) %>% 
  mutate(isZeroBracketingRate = ifelse(bracketingRate == 0, 1, 0)) %>% 
  summarise(proportionZeroBracketingRate = sum(isZeroBracketingRate) / n()) %>% 
  as.numeric()
```

@@

```{r}
weeklyIndividualSources %>% 
  filter(!is.na(bracketingRate)) %>% 
  mutate(isZeroBracketingRate = ifelse(bracketingRate == 0, 1, 0)) %>% 
  summarise(proportionZeroBracketingRate = sum(isZeroBracketingRate) / n()) %>% 
  as.numeric()
```

@@

A key goal is to identify decisions that provide a net advantage in expected value.
Although there is considerable variability and the outcome is not guaranteed, small advantages can yield considerable gains in the long run [@Tanney2021]; however, one must be able to survive the costs of losses to obtain enough long-term trials.
So, do not bet more than you are willing to lose.
